---
title: "`ggplot2` themes"
---

```{r}
#| include: false

knitr::opts_chunk$set(echo = TRUE, dev = "svg", fig.align = "center")
```

This a quick example to show you how to globally define a theme that can be reused writing less code and improving the consistency in the documents, slides, papers, etc.

When you create a `ggplot2` object, the default theme is the `theme_gray()`:

```{r}
library(ggplot2)

ggplot(iris, aes(x = Sepal.Length, y = Petal.Width, color = Species)) +
    geom_point(size = 3) +
    theme_gray()
```

By default, all the theming features can be included with `theme()`:

```{r}
ggplot(iris, aes(x = Sepal.Length, y = Petal.Width, color = Species)) +
    geom_point(size = 3) +
    theme(axis.title.x = element_text(size = 20, face = "bold"))
```

You can avoid copy-and-paste of theming features by creating a new theme function and use the function directly. For example, assume you want:

- bold and larger axis title
- title in the middle of the plot (not left-aligned as default)
- legend always below the plot

```{r}
my_theme <- function(){ # no argument
    theme(
        axis.title = element_text(face = "bold", size = 20),
        legend.position = "bottom",
        plot.title = element_text(hjust = 0.5)
    )
}

ggplot(iris, aes(x = Sepal.Length, y = Petal.Width, color = Species)) +
    geom_point(size = 3) +
    ggtitle("my amazing plot") +
    my_theme()
```

You can easily add other elements to `my_theme()` and also save the function and import it with `source()` in other scripts.

An even more general approach is changing, within a script or document, the default theme thus all the next plots will have your custom theme by default.

```{r}
theme_set(my_theme())

# note that I removed my_theme()
ggplot(iris, aes(x = Sepal.Length, y = Petal.Width, color = Species)) +
    geom_point(size = 3) +
    ggtitle("my amazing plot")
```

Finally, you can set the font size consistently with a combination of setting the base size of a plot and adjusting the relative size with `rel()`. For example, I set the base size to `24pt` and I made the legend text a little bit smaller and the title a little bit bigger.

```{r}
my_theme <- function(){ # no argument
    theme_minimal() +
        theme(
        text = element_text(size = 24), # this is the general text
        axis.title = element_text(face = "bold"),
        legend.position = "bottom",
        plot.title = element_text(hjust = 0.5, size = rel(1.2)),
        legend.text = element_text(size = rel(0.8))
    )
}

ggplot(iris, aes(x = Sepal.Length, y = Petal.Width, color = Species)) +
    geom_point(size = 3) +
    ggtitle("my amazing plot") +
    my_theme()
```