---
title: "Quarto Presentation"
subtitle: "Example"
institute: University of Padova
bibliography: "https://raw.githubusercontent.com/filippogambarota/bib-database/main/references.bib"
csl: "https://raw.githubusercontent.com/citation-style-language/styles/master/apa.csl"
author: 
  - name: "Filippo Gambarota"
    email: filippo.gambarota@unipd.it
    github: filippogambarota
    orcid: "0000-0002-6666-1747"
format: 
    revealjs: default
#    minimal-revealjs: default
#    beamer: default
---

# Section

## Markdown

## Figures

You can use `R` to directly include figures without external files.

```{r}
#| echo: true
#| label: ggplot-example
#| eval: false
library(ggplot2)
iris |> 
    ggplot(aes(x = Sepal.Length, y = Petal.Width, color = Species)) +
    geom_point(size = 3) +
    geom_smooth(method = "lm", se = FALSE) +
    theme_minimal(20) +
    theme(legend.position = "bottom")
```

## Figures

You can use `R` to directly include figures without external files.

```{r}
#| label: ggplot-example
#| fig-height: 5
```

## Citations

You can easily include citations using the BibTeX format. For example you can cite using `[@key]`, thus `[@Klau2023-sb]` will be rendered as [@Klau2023-sb]. In addition there will be a references slide at the end of the presentation.

## Bullets

You can easily include bullets (with and without numbering) using:

```
- element 1
- element 2
- element 3
```

Or

```
1. element 1
2. element 2
3. element 3
```

## Bullets

You can easily include bullets (with and without numbering) using:

- element 1
- element 2
- element 3

Or

1. element 1
2. element 2
3. element 3

## Bullets

You can also set the incremental bullets:

:::{.incremental}
- element 1
- element 2
- element 3
:::

. . .

Or

:::{.incremental}
1. element 1
2. element 2
3. element 3
:::

## References